```{r}
options(
        stringsAsFactors = FALSE, 
        scipen=10)
# if(!require(checkpoint)) install.packages("checkpoint");library(checkpoint)
#'checkpoint('2016-12-13')
snapshotDate = '2017-06-18'
# checkpoint(snapshotDate)
# setSnapshot(snapshotDate)
options(repos = c(CRAN = paste0('https://mran.microsoft.com/snapshot/', snapshotDate)))
assign('.lib.loc', 
       c(path.expand(paste0('~/.checkpoint/', snapshotDate, '/lib/', version$platform, '/', version$major, '.', version$minor)), path.expand(paste0('~/.checkpoint/R-', version$major, '.', version$minor)), .Library.site), 
       envir = environment(.libPaths))

# devtools::install_github('MatthieuStigler/RDDtools/RDDtools')
# install.packages(c('rdrobust','rdlocrand', 'rddensity'))
#'library(rdd)
#'library(rdrobust)
#'library(rdlocrand)
#'library(rddensity)

library(tidyverse)
library(RDDtools)
library(data.table)
library(dtplyr)
library(magrittr)
library(gridExtra)
library(broom)
library(stringr)
library(janitor)
# library(rlist)
library(readxl)
library(haven)
library(sjlabelled)
library(rio)
# library(texreg)
library(doMC)
library(foreach)
library(pbapply)
library(stargazer)

sumtab = function(df) summary(df) %>% data.frame %>% select(variables = Var2, Freq) %>% separate(Freq, c('stats', 'val'), ':')  %>% spread(key = stats, val) %>%  .[,c(1,5,7,4,2,6,3,8)]
```


```{r}
susenas_hh_prep <- function(filepath, label = NULL) 
{
ssn_hh = import(filepath)
if(!is.null(label)) ssn_hh %<>% sjmisc::set_label(ssn_hh_lab)
ssn_hh %<>% janitor::clean_names

ssn_hh %<>% mutate(  pkhever = ifelse(b7r2a == 1, 1, 0)
                   , bsmever = ifelse(  b7r6a == 1 
                                      | b7r6b == 1 
                                      | b7r6c == 1 
                                      | b7r6d == 1
                                      , 1, 0)
                   , pbiever = ifelse(b7r8a == 1, 1, 0)
                   )
ssh_hh
}

ssn_hh_lab = read_excel('~/Seafile/Susenas/Susenas2013/Layout Susenas gab 2013.xls', skip = 4)  
ssn_hh_lab %>% data.table
ssn_hh_lab %<>% .[c(ssn_hh_lab$Label, 'Expenditure/capita', 'Food Exp/capita', 'Non Food Exp /capita')-nrow(.),]

ssn_hh %>% group_by(b1r1) %>% summarise(pkhever = sum(pkhever)) %>% summarise(sum(pkhever != 0)) #33

ssn_hh %>% group_by(b1r1, b1r2) %>% summarise(pkhever = sum(pkhever)) %>% ungroup %>% summarise(sum(pkhever != 0)) #292


susenas_id_prep <- function(filepath, label = NULL) 
{
ssn_id = import(filepath)
if(!is.null(label)) ssn_id %<>% sjmisc::set_label(ssn_id_lab)
ssn_id %<>% janitor::clean_names

ssn_id %<>% mutate(pkhever = ifelse(b7r2a == 1, 1, 0)
                   , ever_prim = ifelse(b5r15 >= 4)
                   , ever_middle = ifelse(b5r15 >= 4)
                   )
ssh_id
}
```

# SUSENAS 2013


```{r}
s13h = import('~/Seafile/Susenas2013/kor13rt.dbf')
k13h = read_excel('~/Seafile/Susenas2013/Layout Susenas gab 2013.xls', skip = 4)  %>% .[-nrow(.),]
s13h %<>% set_label(c(k13h$Label, 'Expenditure/capita', 'Food Exp/capita', 'Non Food Exp /capita'))
names(s13h) %<>% tolower

s13h %<>% mutate(pkhever = ifelse(b7r2a == 1, 1, 0))
s13h %<>% mutate(bsmever = ifelse(b7r6a == 1 | b7r6b ==1 | b7r6c ==1 | b7r6d ==1, 1, 0))
s13h %<>% mutate(pbiever = ifelse(b7r8a == 2, 0, 1))

s13h %>% group_by(b1r1) %>% summarise(pkhever = sum(pkhever)) %>% summarise(sum(pkhever != 0)) #33

s13h %>% group_by(b1r1, b1r2) %>% summarise(pkhever = sum(pkhever)) %>% ungroup %>% summarise(sum(pkhever != 0)) #292

s13h %<>%  mutate(percentile = cut(exp_cap, quantile(exp_cap, seq(0,1,.01)), labels=FALSE)) 

s13h = pmt_vars_prep(s13h,s13i) 
s13h =
s13i %>% 
    group_by(urut) %>% 
    summarise(  elig_child018 = 1*(sum(hb == 3 & umur <= 18) > 0)
              )  %>%  
 inner_join(s13h, .)

s13i = import('~/Seafile/Susenas2013/kor13ind.dbf')
names(s13i) %<>% tolower
k13i = c(k14i$Label, 'Exp', 'Food', 'Non Food')
s13i %<>% set_label(k13i)

s13i = 
s13h %>% 
    dplyr::select(urut, percentile, pkhever, bsmever, pbiever) %>%  
    inner_join(s13i) 

s13i %<>% mutate(jk = ifelse(jk ==2, 0, jk))

s13i %<>% 
 mutate(  sick_1m = ifelse(b5r1a ==1 | b5r1b ==1 | b5r1c ==1 | b5r1d ==1 | b5r1e ==1 | b5r1f ==1 | b5r1g ==1 | b5r1h ==1 , 1, 0)
        , sick_fever = ifelse(b5r1a ==2, 0, 1)
        , sick_cough = ifelse(b5r1b ==2, 0, 1)
        , sick_cold = ifelse(b5r1c ==2, 0, 1)
        , sick_asthma = ifelse(b5r1d ==2, 0, 1)
        , sick_diarrhea = ifelse(b5r1e ==2, 0, 1)
        , sick_headache = ifelse(b5r1f ==2, 0, 1)
        , sick_toothache = ifelse(b5r1g ==2, 0, 1)
        , sick_other = ifelse(b5r1a ==2, 0, 1)
        , sick_selfmed = ifelse(b5r4a ==2, 0, 1)
        , out_1m = ifelse(b5r5 ==2, 0, 1) 
        , out_hosp = ifelse(b5r6a > 0 | b5r6b > 0, 1, 0)
        , out_hosp_pub = ifelse(b5r6a > 0, 1, 0)
        , out_pub = ifelse(b5r6a > 0 | b5r6d > 0, 1, 0)
        , out_priv = ifelse(b5r6b > 0 | b5r6c > 0, 1, 0)
        , out_6m = ifelse(b5r7 ==2, 0, b5r7)
        , in_1y = ifelse(b5r8 ==2, 0, b5r8)
        , in_hosp = ifelse(b5r9a > 0 | b5r9b > 0, 1, 0)
        , in_hosp_pub = ifelse(b5r9a > 0, 1, 0)
        , in_hosp_priv = ifelse(b5r9b > 0 , 1, 0)
        , in_pub = ifelse(b5r9a > 0 | b5r9c > 0, 1, 0)
        , in_pub_healthc = ifelse(b5r9c > 0, 1, 0)
        )
```



# SUSENAS 2014

```{r}

s14h = import('~/Seafile/Susenas2014/2014Gab_kor14rt.dbf')
k14h = read_excel('~/Seafile/Susenas2014/Layout Kor Modul 2014 GABUNGAN.xls', skip = 1, sheet = 3)  
s14h %<>% set_label(k14h$Label)
names(s14h) %<>% tolower
s14h %<>% mutate(pkhever = ifelse(b7r2a == 1, 1, 0),
                 bsmever = ifelse(b7r6a == 1 | b7r6b ==1 | b7r6c ==1 | b7r6d ==1, 1, 0),
                 pbiever = ifelse(b7r8a == 2, 0, 1))
                 

s14h %>% group_by(b1r1) %>% summarise(pkhever = sum(pkhever)) %>% summarise(sum(pkhever != 0)) #33
s14h %>% group_by(b1r1, b1r2) %>% summarise(pkhever = sum(pkhever)) %>% ungroup %>% summarise(sum(pkhever != 0)) #380

s14i = import('~/Seafile/Susenas2014/kor14ind_rev2_230915.dbf')
k14i = read_excel('~/Seafile/Susenas2014/Layout Kor Modul 2014 GABUNGAN.xls', skip = 1, sheet = 1)  
s14i %<>% set_label(k14i$Label)
names(s14i) %<>% tolower
s14i = 
s14h %>% 
    select(urut, pkhever, bsmever, pbiever) %>%  
    inner_join(s14i, by='urut') 

s14i %<>% mutate(jk = ifelse(jk ==2, 0, jk))

s14i %<>% 
 mutate(  sick_1m = ifelse(b5r1a ==1 | b5r1b ==1 | b5r1c ==1 | b5r1d ==1 | b5r1e ==1 | b5r1f ==1 | b5r1g ==1 | b5r1h ==1 , 1, 0)
        , sick_fever = ifelse(b5r1a ==2, 0, 1)
        , sick_cough = ifelse(b5r1b ==2, 0, 1)
        , sick_cold = ifelse(b5r1c ==2, 0, 1)
        , sick_asthma = ifelse(b5r1d ==2, 0, 1)
        , sick_diarrhea = ifelse(b5r1e ==2, 0, 1)
        , sick_headache = ifelse(b5r1f ==2, 0, 1)
        , sick_toothache = ifelse(b5r1g ==2, 0, 1)
        , sick_other = ifelse(b5r1a ==2, 0, 1)
        , sick_selfmed = ifelse(b5r4a ==2, 0, 1)
        , out_1m = ifelse(b5r5 ==2, 0, 1) 
        , out_hosp = ifelse(b5r6a > 0 | b5r6b > 0, 1, 0)
        , out_hosp_pub = ifelse(b5r6a > 0, 1, 0)
        , out_pub = ifelse(b5r6a > 0 | b5r6d > 0, 1, 0)
        , out_priv = ifelse(b5r6b > 0 | b5r6c > 0, 1, 0)
        , out_6m = ifelse(b5r7 ==2, 0, b5r7)
        , in_1y = ifelse(b5r8 ==2, 0, b5r8)
        , in_hosp = ifelse(b5r9a > 0 | b5r9b > 0, 1, 0)
        , in_hosp_pub = ifelse(b5r9a > 0, 1, 0)
        , in_hosp_priv = ifelse(b5r9b > 0 , 1, 0)
        , in_pub = ifelse(b5r9a > 0 | b5r9c > 0, 1, 0)
        , in_pub_healthc = ifelse(b5r9c > 0, 1, 0)
        )

```
29 percent of household in 2014 had jamkesmas, 36 percent of sample had either jamkesmas or jamkesda.
janitor::tabyl(s14h\$b7r8a)
s14h\$b7r8a      n   percent
1          1  81742 0.2864121
2          2 203658 0.7135879
janitor::tabyl(s14h\$b7r8b)
s14h\$b7r8b      n    percent
1          1  27195 0.09528732
2          2 258205 0.90471268
s14h %\$% sum(b7r8b == 1 | b7r8a ==1)
[1] 103752
summary(s14pkh\$fwt_tahun)
Min. 1st Qu.  Median    Mean 3rd Qu.    Max.
1.00   75.96  153.10  230.60  324.90 2834.00
# 
sum(s14pkh\$fwt_tahun)
[1] 8,045,772

# SUSENAS 2015

```{r}

s15h = read_dta('~/Seafile/2015Q1_Said/kor15rt.dta')
k15h = read_excel('~/Seafile/2015Q1_Said/Docs_ssn_mar2015/Layout_kor15rt.xlsx', skip=3L)
k15hv = k15h[1:94,]
k15hv %<>% clean_names %>%  mutate(variable=tolower(variable))
k15hv %<>% rbind(c('catatan',95, 'Catatan'), c('exp_cap',96, 'Expenditure per capita'))
s15h %<>% set_label(k15hv$label)

s15i = read_dta('~/Seafile/2015Q1_Said/kor15ind.dta')
k15i = read_excel('~/Seafile/2015Q1_Said/Docs_ssn_mar2015/Layout_kor15ind.xlsx', skip = 4L)
k15i %<>% .[1:208,1:4]
k15i[207,] = c('catatan', 207, 'Catatan', 'Text')
k15i[208,] = c('exp_cap', 208, 'Household expenditure per capita', 'Scale')
s15i %<>% set_label(k15i$Label)
s15i %>% group_by(urut) %>%  summarise(npbi = sum(r711d)) %>% summarise(sum(npbi > 0))
s15i %$%  {sum(r711d*fwt_tahun)/sum(fwt_tahun)}

s15i %>% group_by(urut) %>%  summarise(npbi = sum(r711d)) %>% summarise(sum((npbi > 0)*fwt_tahun)/sum(fwt_tahun))
```

aggregate(exp_cap ~ r1606, s15h, quantile)
r1606  exp_cap.0% exp_cap.25% exp_cap.50% exp_cap.75% exp_cap.100%
    1     1    91395.24   338446.55   452980.24   624778.17  94873301.43
2     5    90762.62   451016.29   684038.83  1085365.97  64338952.38
 
quantile(s15h\$exp_cap)
s15h\$exp_cap
0%         25%         50%         75%        100%
    90762.62   429877.18   650538.93  1030743.15 94873301.43
 

# MERGE PMT SCORES


```{r}

s14h %<>% 
    left_join( dplyr::select(pmt14, urut, scores) )
s14i %<>% 
    left_join( dplyr::select(pmt14, urut, scores) )
s13h %<>% 
    inner_join( dplyr::select(pmt13, urut, scores) )
s13i %<>% 
    inner_join( dplyr::select(pmt13, urut, scores) )
s13i %<>% mutate(jk = ifelse(jk ==2, 0, jk))

```


# SUBSAMPLES

## Child Age 0 to 4

### 2014

```{r}

s14i %$% crosstab(umur, is.na(b5r10a))
s14i_child = 
    s14i %>%  
    filter(umur %in% 0:4) %>% 
    dplyr::select(  urut, nart, jk, pkhever, bsmever, pbiever, scores, kabu , umur
           , agem = b5r10a
           , aged = b5r10b
           , asst_born1 = b5r11a
           , asst_born2 = b5r11b
           , vac_bcg = b5r12a
           , vac_dpt = b5r12b
           , vac_pol = b5r12c
           , vac_cam = b5r12d
           , vac_hep = b5r12e
           , bfed_ev = b5r13a
           , bfed_dur = b5r13b1
           , bfed_exc = b5r13b2
           , bfed_nex = b5r13b3
           ) 
s14i_child %<>% mutate(  med_born2 = ifelse(asst_born2 %in% 1:3, 1, 0) 
                    , med_born1 = ifelse(asst_born1 %in% 1:3, 1, 0)
                    , vac_dpt3 = ifelse(vac_dpt %in% 3:6, 1, 0)
                    , vac_pol3 = ifelse(vac_pol %in% 3:6, 1, 0)
                    , vac_hep3 = ifelse(vac_hep %in% 3:6, 1, 0)
                    )

```

### 2013

```{r}


s13i_child = 
    s13i %>%  
    filter(umur %in% 0:4) %>% 
    dplyr::select(  urut, nart, jk, pkhever, bsmever, pbiever, scores, kabu , umur
           , agem = b5r10a
           , aged = b5r10b
           , asst_born1 = b5r11a
           , asst_born2 = b5r11b
           , vac_bcg = b5r12a
           , vac_dpt = b5r12b
           , vac_pol = b5r12c
           , vac_cam = b5r12d
           , vac_hep = b5r12e
           , bfed_ev = b5r13a
           , bfed_dur = b5r13b1
           , bfed_exc = b5r13b2
           , bfed_nex = b5r13b3
           ) 
s13i_child %<>% mutate(  med_born2 = ifelse(asst_born2 %in% 1:3, 1, 0) 
                    , med_born1 = ifelse(asst_born1 %in% 1:3, 1, 0)
                    , vac_dpt3 = ifelse(vac_dpt %in% 3:6, 1, 0)
                    , vac_pol3 = ifelse(vac_pol %in% 3:6, 1, 0)
                    , vac_hep3 = ifelse(vac_hep %in% 3:6, 1, 0)
                    )

```


## School Age: 5+

### Susenas 2014
           

```{r}
s14i_school = 
    filter(s14i, umur >= 5) 

s14i_school =
    mutate(  s14i_school
           , ever_school = ifelse(b5r14 > 1, 1, 0)
           , ever_prim = ifelse(b5r15 >= 1, 1, 0)
           , ever_middle = ifelse(b5r15 >= 4, 1, 0)
           , ever_high = ifelse(b5r15 >= 7, 1, 0)
           , ever_col = ifelse(b5r15 >= 11, 1, 0)
           , grad_prim = ifelse(b5r17 >= 2, 1, 0)
           , grad_middle = ifelse(b5r17 >= 5, 1, 0)
           , grad_high = ifelse(b5r17 >= 8, 1, 0)
           , grad_col = ifelse(b5r17 >= 12, 1, 0)
           ) 

s14i_school =
    mutate_at(  s14i_school 
              , vars(starts_with('ever_'), starts_with('grad_'))
              , funs(ifelse(is.na(.), 0, .))
              )

s14i_school %<>% 
    mutate(edu_lev = cut(b5r15, breaks = c(0,3,6,10,14), labels = F) , 
           edu_lev = dplyr::recode_factor(edu_lev, 
                                          'Primary', 'Middle', 'High', 'College', 
                                          .missing = 'Never'))

s14i_school %<>% 
    mutate(b5r16 = as.numeric(ifelse(is.na(b5r16), 0, b5r16)), edu_year = 
           dplyr::case_when(  b5r15 %in% 1:3   & b5r16 >=6 ~ 6
                            , b5r15 %in% 1:3   & b5r16 < 6 ~ b5r16
                            , b5r15 %in% 4:6   & b5r16 >=3 ~ 9
                            , b5r15 %in% 4:6   & b5r16 < 3 ~ b5r16 + 6
                            , b5r15 %in% 7:10  & b5r16 >=3 ~ 12
                            , b5r15 %in% 7:10  & b5r16 < 3 ~ b5r16 + 9
                            , b5r15 %in% 11:15 & b5r16 >=5 ~ 17
                            , b5r15 %in% 11:15 & b5r16 < 5 ~ b5r16 + 12
                         ))

s14i_school = 
    left_join(s14i_school, 
              select(pkh_kab, kabu = idkabu, pkh_start ))

s14i_school = mutate(s14i_school, 
                       pkhever = factor(pkhever, 
                                        levels = c(0,1), 
                                        labels = c('Non PKH', 'PKH')))
```


### Susenas 2013

```{r}

s13i_school =
    filter(s13i, umur >= 5) 
   
s13i_school %<>% 
    mutate(edu_lev = cut(b5r15, breaks = c(0,3,6,10,14), labels = F) , 
           edu_lev = dplyr::recode_factor(edu_lev, 
                                          'Primary', 'Middle', 'High', 'College', 
                                          .missing = 'Never'))

s13i_school = 
    mutate(s13i_school
           , b5r16 = as.numeric(ifelse(is.na(b5r16), 0, b5r16))
           , edu_year = 
               dplyr::case_when(  b5r15 %in% 1:3   & b5r16 >=6 ~ 6
                                , b5r15 %in% 1:3   & b5r16 < 6 ~ b5r16
                                , b5r15 %in% 4:6   & b5r16 >=3 ~ 9
                                , b5r15 %in% 4:6   & b5r16 < 3 ~ b5r16 + 6
                                , b5r15 %in% 7:10  & b5r16 >=3 ~ 12
                                , b5r15 %in% 7:10  & b5r16 < 3 ~ b5r16 + 9
                                , b5r15 %in% 11:15 & b5r16 >=5 ~ 17
                                , b5r15 %in% 11:15 & b5r16 < 5 ~ b5r16 + 12
                                ))

s13i_school =
    mutate(  s13i_school
           , ever_school = ifelse(b5r14 > 1, 1, 0)
           , ever_prim = ifelse(b5r15 >= 1, 1, 0)
           , ever_middle = ifelse(b5r15 >= 4, 1, 0)
           , ever_high = ifelse(b5r15 >= 7, 1, 0)
           , ever_col = ifelse(b5r15 >= 11, 1, 0)
           , grad_prim = ifelse(b5r17 >= 2, 1, 0)
           , grad_middle = ifelse(b5r17 >= 5, 1, 0)
           , grad_high = ifelse(b5r17 >= 8, 1, 0)
           , grad_col = ifelse(b5r17 >= 12, 1, 0)
           ) 

s13i_school =
    mutate_at(  s13i_school 
              , vars(starts_with('ever_'), starts_with('grad_'))
              , funs(ifelse(is.na(.), 0, .))
              )

s13i_school = 
    mutate(s13i_school
           , drop_prim = ifelse(edu_lev != 'Primary', NA, ifelse(grad_prim == 0, 1, 0))
           , drop_middle = ifelse(edu_lev != 'Middle', NA, ifelse(grad_middle == 0, 1, 0))
           , drop_high = ifelse(edu_lev != 'High', NA, ifelse(grad_high == 0, 1, 0))
           , drop_col = ifelse(edu_lev != 'College', NA, ifelse(grad_col == 0, 1, 0))
           )

s13i_school = 
    left_join(s13i_school, 
              select(pkh_kab, kabu = idkabu, pkh_start ))

s13i_school = mutate(s13i_school, 
                       pkhever = factor(pkhever, 
                                        levels = c(0,1), 
                                        labels = c('Non PKH', 'PKH')))
s13i_school %<>% mutate(status = cut(percentile, c(0,20,40,60,80,100), c('poorest', 'poor', 'middle', 'rich', 'richest'))) 

s13i_school = dplyr::select(  s13i_school, urut, nart, jk, pkhever, bsmever, pbiever, kabu , umur, edu_lev, edu_year, starts_with('grad_'), starts_with('ever_'), starts_with('drop'), exp_cap, percentile, status) 

```

